---
title: "01_Step3"
author: "zagor"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: yes
    self_contained: yes
    fig_width: 16
    fig_height: 16
    toc: yes
    toc_depth: 5
    number_sections: yes
    theme: flatly
    highlight: tango
  pdf_document:
    toc: yes
    toc_depth: '5'
  word_document:
    toc: yes
    toc_depth: '5'
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(#dev = c('pdf', 'png'),  # this embeds pdf and crates scrolable blocks
                      dev = c('png'), 
                      fig.align = 'center', 
                      fig.height = 16, 
                      fig.width = 16 ,
                      warning = FALSE, message = FALSE
                      )
# options(knitr.table.format = "html")

```

Customise palettes and shapes according to the data structure.

```{r, libraries.sources1}

rm(list = ls(all = TRUE))
source('01_f-ctions.R')

```


Data files structure: 1st column is SampleName (link to phenodata), followed by measured variables

Path to data: ../input/

```{r}

fp = file.path('..', 'input')
list.files(fp, pattern = '.txt$')

```

Path to Phenodata: ../../../

```{r}

fp = file.path('..', '..', '..')
list.files(fp, pattern = '.txt$')

```

There may be multiple phenodata versions (see [pISA-tree INSTRUCTIONS.pdf](https://github.com/NIB-SI/pISA-tree/blob/projects/INSTRUCTIONS.pdf)

In this caste, SampleName is created as: Treatment_Day_PlantNoNo



```{r}

fn = 'phenodata_20221001.txt'
pheno = data.table::fread(file.path(fp, fn), header = TRUE)
data.table::setDF(pheno)

pheno = pheno[, grep('^SampleName$|^Treatment$|^SamplingDay$|^PlantNo$', colnames(pheno))]
head(pheno)
tail(pheno)

table(pheno$Treatment, pheno$SamplingDay)

```

Each condition has 4 replicates



# tissue: leaves

## Omics level: hormonomics

```{r}

tissue = 'Leaves'
o.l. = 'Hormonomics'

```


### Read data

```{r, 030_hormonomics, echo=TRUE}

fpi = file.path('..', 'input')
fn = 'data_hormonomics.txt'
horm = data.table::fread(file.path(fpi, fn), header = TRUE)
data.table::setDF(horm)

horm = merge(pheno, 
             horm, 
             by = 'SampleName', 
             all.x = FALSE, 
             all.y = TRUE)
horm = horm[, -grep('SampleName', colnames(horm))]

horm$SamplingDay = as.numeric(horm$SamplingDay)
horm$Treatment = factor(horm$Treatment)
horm = horm[order(horm$Treatment, horm$SamplingDay, horm$PlantNo), ]

horm.long = reshape2::melt(horm[, -c(grep('PlantNo', colnames(horm)))], id.vars=c("Treatment",   "SamplingDay"))
horm.long$SamplingDay = as.numeric(horm.long$SamplingDay)
keep2 = grep('PlantNo|Treatment|SamplingDay', colnames(horm), invert = TRUE)

```


### Plot data with ggplot


```{r, 031_hormonomics.ggplot, echo=TRUE}


myplot.ggplot(df = horm.long, x = horm.long$Treatment, y = horm.long$value, 
              ncol = ceiling(length(levels(horm.long$variable))/2), 
              scales.y = "free_y", 
              title = stringr::str_c(o.l., 
                                     '\n', 
                                     stringr::str_c(unique(horm.long$Treatment), collapse=', '),
                                     collapse='' ), 
              xlab = 'Treatment', 
              ylab = 'value', 
              palette = my.ggplot.palette)

graphs = horm.long %>%
  dplyr::group_by(variable) %>%
  rstatix::doo(
    ~ggpubr::ggdotplot(
      data =., 
      x = "SamplingDay", 
      y = "value",
      fill = "Treatment", 
      palette = my.ggplot.palette, 
      legend = "none",
      add = c("jitter", "mean_sd"),
      position = position_jitter(0.05),
      ggtheme = ggpubr::theme_pubr(),
      facet.by = c("Treatment")
      )
      , result = "plots"
    )

variable = levels(graphs$variable)
plots = graphs$plots %>% set_names(variable)
for(var in variable){
  graph.i = plots[[var]] +
    labs(title = var)
  print(graph.i)
} 


```

### NMDS

#### On all

```{r, 032_hormonomics.nmds, echo=TRUE}

subset = horm
mymat = subset[, keep2]
time.levels = sort(as.numeric(unique(subset$SamplingDay)))
stress.levels = levels(subset$Treatment)
k = 3

NMDS.plots = my.NMDS(mymat = mymat, 
                     subset = subset, 
                     stress.levels = stress.levels,
                     time.levels = time.levels,
                     title = o.l.,
                     k = k) # dimensions

if (k == 3){
  cowplot::plot_grid(NMDS.plots[[1]], NMDS.plots[[2]], NMDS.plots[[3]],  
                     NMDS.plots[[4]], NMDS.plots[[5]], NMDS.plots[[6]],
                     ncol=3, nrow = 2)
} else {
  cowplot::plot_grid(NMDS.plots[[1]])
}



```


#### Specific Condition


```{r}

subset = horm[horm$SamplingDay %in% time.levels[c(1, 4)], ]
mymat = subset[, keep2]
time.levels = sort(as.numeric(unique(subset$SamplingDay)))
stress.levels = levels(subset$Treatment)
k = 3

NMDS.plots = my.NMDS(mymat = mymat, 
                     subset = subset, 
                     stress.levels = stress.levels,
                     time.levels = time.levels,
                     title = o.l.,
                     k = k) # dimensions

if (k == 3){
  cowplot::plot_grid(NMDS.plots[[1]], NMDS.plots[[2]], NMDS.plots[[3]],  
                     NMDS.plots[[4]], NMDS.plots[[5]], NMDS.plots[[6]],
                     ncol=3, nrow = 2)
} else {
  cowplot::plot_grid(NMDS.plots[[1]])
}



subset = horm[horm$Treatment %in% stress.levels[2], ]
mymat = subset[, keep2]
time.levels = sort(as.numeric(unique(subset$SamplingDay)))
stress.levels = levels(subset$Treatment)
k = 2

NMDS.plots = my.NMDS(mymat = mymat, 
                     subset = subset, 
                     stress.levels = stress.levels,
                     time.levels = time.levels,
                     title = o.l.,
                     k = k) # dimensions

if (k == 3){
  cowplot::plot_grid(NMDS.plots[[1]], NMDS.plots[[2]], NMDS.plots[[3]],  
                     NMDS.plots[[4]], NMDS.plots[[5]], NMDS.plots[[6]],
                     ncol=3, nrow = 2)
} else {
  cowplot::plot_grid(NMDS.plots[[1]])
}



```


### correlation

```{r, 033_hormonomics.cor, echo=TRUE}

par(mfrow = c(2,2))
my.cor.plot(mymat = as.matrix(horm[, keep2]), 
            main = paste(o.l., '(all tp)'), 
            col = rev(my.heatmap.col1), 
            order = 'original', 
            type = 'pearson', 
            choose = 1)
my.cor.plot(mymat = as.matrix(horm[, keep2]), 
            main = paste(o.l., '(all tp)'), 
            col = rev(my.heatmap.col2), 
            order = 'original', 
            type = 'pearson', 
            choose = 1)
my.cor.plot(mymat = as.matrix(horm[, keep2]), 
            main = paste(o.l., '(all tp)'), 
            col = rev(my.heatmap.col1), 
            order = 'hclust', 
            type = 'pearson', 
            choose = 2)
my.cor.plot(mymat = as.matrix(horm[, keep2]), 
            main = paste(o.l., '(all tp)'), 
            col = rev(my.heatmap.col2), 
            order = 'hclust', 
            type = 'pearson', 
            choose = 2)
par(mfrow = c(1,1))



my.pairs.panels(df = as.matrix(horm[, keep2]), 
                method = "pearson", 
                palette = my.ggplot.palette, 
                scale = FALSE,
                main = paste(o.l., '(all tp)'),
                cex.labels = 1, 
                cex = 1)


```


### cor groups

Here we have one Control and one Stress level - adapt as needed

```{r, 034_hormonomics.cor.groups, echo=TRUE}

print(stress.levels)
Ctrl = as.matrix(horm[horm$Treatment == stress.levels[1], keep2])
Stress = as.matrix(horm[horm$Treatment == stress.levels[2], keep2])

par(mfrow=c(2,2))
my.cor.plot(mymat = Ctrl,
            main = 'pearson cor (all tp)\nCtrl',
            col = rev(my.heatmap.col1),
            order = 'original',
            type = 'pearson',
            choose = 1)
my.cor.plot(mymat = Stress,
            main = 'pearson cor (all tp)\nStress',
            col = rev(my.heatmap.col1),
            order = 'original',
            type = 'pearson',
            choose = 1)

my.cor.plot(mymat = Ctrl,
            main = 'pearson cor (all tp)\nCtrl',
            col = rev(my.heatmap.col2),
            order = 'original',
            type = 'pearson',
            choose = 1)
my.cor.plot(mymat = Stress,
            main = 'pearson cor (all tp)\nStress',
            col = rev(my.heatmap.col2),
            order = 'original',
            type = 'pearson',
            choose = 1)
par(mfrow=c(1,1))


palCS = rainbow(length(time.levels))[as.numeric(as.factor(horm[horm$Treatment == stress.levels[1], 2]))]
pie(rep(1, length(time.levels)), 
    col = unique(palCS), 
    labels = unique(horm[horm$Treatment == stress.levels[1], 2]), 
    main = paste(stress.levels, collapse = ' '))


my.pairs.panels(df = Ctrl, 
                method = "pearson", 
                palette = palCS, 
                scale = FALSE,
                main = 'horm Ctrl (all tp)',
                cex.labels = 1.0, 
                cex = 1)
my.pairs.panels(df = Stress, 
                method = "pearson", 
                palette = palCS, 
                scale = FALSE,
                main = 'horm Stress (all tp)',
                cex.labels = 1.0, 
                cex = 1)



```


### cor dist

#### At specific time points

```{r, echo=TRUE}


Ctrl = (horm[(horm$Treatment == stress.levels[1]) & 
               (horm$SamplingDay %in% time.levels[c(1, 4)]), 1:ncol(horm)])
Stress =  (horm[(horm$Treatment == stress.levels[2]) & 
                  (horm$SamplingDay %in% time.levels[c(1, 4)]), 1:ncol(horm)])

Ctrl[Ctrl$SamplingDay != 1,]$SamplingDay = 2
Stress[Stress$SamplingDay != 1,]$SamplingDay = 2


```




```{r, 035_hormonomics.cor.dist, echo=TRUE}

my.c.list = list (cor(Ctrl[, keep2], use = 'na.or.complete'), 
                  cor(Stress[, keep2], use = 'na.or.complete'))
names(my.c.list) = c('Ctrl', 'Stress')


comb = RcppAlgos::comboGrid(1:length(my.c.list), 1:length(my.c.list),  repetition = FALSE)

for (i in 1:nrow(comb)){
  

  cat('blue'(names(my.c.list)[comb[i,1]], names(my.c.list)[comb[i,2]], '\n'))
  a = my.c.list[[comb[i,1]]]
  b = my.c.list[[comb[i,2]]]

  plot = my.pheatmap(df = a, 
                      main = names(my.c.list)[comb[i,1]], 
                      col = rev(my.heatmap.col1),
                      breaks = setdiff(seq(-1, 1, 0.1), 0),
                     silent = TRUE) 
  myplots = list(plot[[4]])
  plot = my.pheatmap(df = a, 
                      main = names(my.c.list)[comb[i,1]], 
                      col = rev(my.heatmap.col2),
                      breaks = setdiff(seq(-1, 1, 0.1), 0),
                     silent = TRUE) 
  myplots[[2]] = (plot[[4]])
  
  
  plot = my.pheatmap(df = b, 
                      main = names(my.c.list)[comb[i,2]], 
                      col = rev(my.heatmap.col1),
                      breaks = setdiff(seq(-1, 1, 0.1), 0),
                     silent = TRUE) 
  myplots[[3]] = (plot[[4]])
  plot = my.pheatmap(df = b, 
                      main = names(my.c.list)[comb[i,2]], 
                      col = rev(my.heatmap.col2),
                      breaks = setdiff(seq(-1, 1, 0.1), 0),
                     silent = TRUE) 
  myplots[[4]] = (plot[[4]])
  

  diff = abs(a - b)
  plot = my.pheatmap(df = diff,
                      col = rev(my.dist.col), 
                      main = paste0('Diffrence ', 
                                    names(my.c.list)[comb[i,1]], ' - ', 
                                    names(my.c.list)[comb[i,2]]),
                      breaks = seq(0, 2, 0.2),
                     silent = TRUE)
  myplots[[5]] = (plot[[4]])
  plot = my.pheatmap(df = diff,
                      col = rev(my.dist.col2), 
                      main = paste0('Diffrence ', 
                                    names(my.c.list)[comb[i,1]], ' - ', 
                                    names(my.c.list)[comb[i,2]]),
                      breaks = seq(0, 2, 0.2),
                     silent = TRUE)
  myplots[[6]] = (plot[[4]])

  gridExtra::grid.arrange(gridExtra::arrangeGrob(myplots[[1]], myplots[[3]], myplots[[5]], ncol=3),
                          gridExtra::arrangeGrob(myplots[[2]], myplots[[4]], myplots[[6]], ncol=3),
                          nrow = 2)

  
  
}


```


### t-tests

```{r, 036_hormonomics.t.tests, echo=TRUE}

data = rbind(Ctrl, Stress)
tmp = c(rep('Ctrl', nrow(Ctrl)),
        rep('Stress', nrow(Stress)))
data$Treatment = tmp
data$Treatment = paste(data$Treatment, data$SamplingDay, sep = '_')

cat(blue('Time defined: 1\n'))
data.1 = data[data$SamplingDay == 1, ]
data.1.1 = data.1[data.1$Treatment %in% c('Ctrl_1', 'Stress_1'), ]
stat.test.1.1 = my.customised.t.test(data = data.1.1[, -grep('PlantNo|SamplingDay', colnames(data.1.1))], 
                                     var.levels = colnames(data.1.1[, keep2]), 
                                     stress.levels = unique(data.1.1$Treatment),
                                     plot.violin = FALSE, 
                                     plot.box = FALSE, 
                                     plot.dot = TRUE,
                                     single = TRUE,
                                     y.lab = o.l.,
                                     p.cex.labels = 1, 
                                     p.cex = 0.5,
                                     p.palette = my.ggplot.palette)


cat(blue('Time defined: 2\n'))
data.2 = data[data$SamplingDay == 2, ]
data.2.1 = data.2[data.2$Treatment %in% c('Ctrl_2', 'Stress_2'), ]
stat.test.2.1 = my.customised.t.test(data = data.2.1[, -grep('PlantNo|SamplingDay', colnames(data.2.1))], 
                                 var.levels = colnames(data.2.1[, keep2]), 
                                 stress.levels = unique(data.2.1$Treatment),
                                 plot.violin = FALSE, 
                                 plot.box = FALSE, 
                                 plot.dot = TRUE,
                                 single = TRUE,
                                 y.lab = o.l.,
                                 p.cex.labels = 1, 
                                 p.cex = 0.5,
                                 p.palette = my.ggplot.palette)


stat.test = rbind(stat.test.1.1,
                  stat.test.2.1)
data.table::setDT(stat.test)
stat.test.leaves.hormonomics = stat.test
ind = (grep('groups', colnames(stat.test.leaves.hormonomics)))
stat.test.leaves.hormonomics = stat.test.leaves.hormonomics[, -..ind]

fpo = file.path('..', 'reports')
fn = paste0(tissue, '-', o.l., '_t.tests.txt')
write.table(stat.test.leaves.hormonomics,
            file = file.path(fpo, fn), 
            append = FALSE, 
            quote = FALSE, 
            sep = "\t",
            eol = "\n", 
            na = "NA", 
            dec = ".", 
            row.names = TRUE,
            col.names = TRUE, 
            qmethod = 'escape',
            fileEncoding = "UTF-8")

```


rcorr Computes a matrix of Pearson's r or Spearman's rho rank correlation coefficients for all possible pairs of columns of a matrix. Missing values are deleted in pairs rather than deleting all rows of x having any missing variables. Ranks are computed using efficient algorithms (see reference 2), using midranks for ties.

### heatmap on Treatment START/STOP (as defined) data


```{r, 037_hormonomics.heatmap.Treatment.groups, echo=TRUE}

my.heatmaply.cor(df = data[, keep2], 
                 type = 'pearson', 
                 dist_method = 'minkowski', 
                 hclust_method = 'ward.D2',
                 main = paste(o.l., 'Treatment [start, stop]\nrcorr, p-val, minkowski, Ward.2'),
                 colors = rev(my.heatmap.col1))
my.heatmaply.cor(df = data[, keep2], 
                 type = 'pearson', 
                 dist_method = 'minkowski', 
                 hclust_method = 'ward.D2',
                 main = paste(o.l., 'Treatment [start, stop]\nrcorr, p-val, minkowski, Ward.2'),
                 colors = rev(my.heatmap.col2))

```



### logFC START/STOP Treatment
 
```{r, 038_plotly.logFC.heatmap, echo=TRUE}


leaf.horm.log2FC = my.logFC(Ctrl = Ctrl,
                            Stress = Stress,  
                            tp = 2, 
                            title = o.l.)


mm = list(
    l = 0,
    r = 0,
    b = 0,
    t = 40
)
m = max(abs(min(leaf.horm.log2FC, na.rm = TRUE)), abs(max(leaf.horm.log2FC, na.rm = TRUE)))
p = plot_ly(z = leaf.horm.log2FC, 
            type = "heatmap",
            y = rownames(leaf.horm.log2FC), 
            x = colnames(leaf.horm.log2FC),
            colors = rev(brewer.pal(n, 'RdBu')),
            zmax = m, 
            zmid = 0, 
            zmin = -m,
            width = 600, 
            height = 300
            ) %>%
  layout(title = 'Leaf Hormonomics', 
         margin = mm)
print(p)

fpo = file.path('..', 'reports')
fn = 'Leaf-Hormonomics_logFC.html'
fn = paste0(tissue, '-', o.l., '_log2FC.html')
saveWidget(p, 
           file = file.path(fpo, fn),
           selfcontained = TRUE)



fn = paste0(tissue, '-', o.l., '_log2FC.txt')
write.table(leaf.horm.log2FC,
            file = file.path(fpo, fn), 
            append = FALSE, 
            quote = FALSE, 
            sep = "\t",
            eol = "\n", 
            na = "NA", 
            dec = ".", 
            row.names = TRUE,
            col.names = TRUE, 
            qmethod = 'escape',
            fileEncoding = "UTF-8")

```



```{r, libraries.sources2}

rm(list=setdiff(ls(), c('pheno',
                        'horm'
                        )))
gc()
source('01_f-ctions.R')
gc()

```



## Omics level: metabolomics

```{r}

tissue = 'Leaves'
o.l. = 'Metabolomics'

```

### Read data

```{r, 040_metabolomics, echo=TRUE}


fpi = file.path('..', 'input')
fn = 'data_metabolomics.txt'
met = data.table::fread(file.path(fpi, fn), header = TRUE)
data.table::setDF(met)

met = merge(pheno, 
             met, 
             by = 'SampleName', 
             all.x = FALSE, 
             all.y = TRUE)
met = met[, -grep('SampleName', colnames(met))]

met$SamplingDay = as.numeric(met$SamplingDay)
met$Treatment = factor(met$Treatment)
met = met[order(met$Treatment, met$SamplingDay, met$PlantNo), ]


```

Repat procedure as for Hormonomics


```{r, libraries.sources3}

rm(list=setdiff(ls(), c('pheno',
                        'horm',
                        'met'
                        )))
gc()
source('01_f-ctions.R')
gc()

```

## Omics level: transcriptomics

```{r}

tissue = 'Leaves'
o.l. = 'Transcriptomics'

```


### Read data

```{r, 050_transcriptomics, echo=TRUE}

fpi = file.path('..', 'input')
fn = 'data_qPCR.txt'
qPCR = data.table::fread(file.path(fpi, fn), header = TRUE)
data.table::setDF(qPCR)

qPCR = merge(pheno, 
             qPCR, 
             by = 'SampleName', 
             all.x = FALSE, 
             all.y = TRUE)
qPCR = qPCR[, -grep('SampleName', colnames(qPCR))]

qPCR$SamplingDay = as.numeric(qPCR$SamplingDay)
qPCR$Treatment = factor(qPCR$Treatment)
qPCR = qPCR[order(qPCR$Treatment, qPCR$SamplingDay, qPCR$PlantNo), ]


```


Repat procedure as for Hormonomics and Metabolomics



```{r, libraries.sources6}

rm(list=setdiff(ls(), c('pheno',
                        'horm',
                        'met',
                        'qPCR'
                        )))
gc()
source('01_f-ctions.R')
gc()

save.image(file = "01.RData")


```



# Multi-Omics

## data

```{r, 60_omics, echo=TRUE}

colM = colnames(met)
colT = colnames(qPCR)
colH = colnames(horm)

omics = merge(qPCR, met, 
              by = c("Treatment", "SamplingDay", "PlantNo"), 
              all.x = FALSE, all.y = FALSE)
omics = merge(omics, horm, 
              by = c("Treatment", "SamplingDay", "PlantNo"), 
              all.x = FALSE, all.y = FALSE)

omics$SamplingDay = as.numeric(omics$SamplingDay)


keep2 = grep("Treatment|SamplingDay|PlantNo", colnames(omics), invert = TRUE)

MT = intersect(keep2,
               which(colnames(omics) %in% c(colM, colT)))
MH = intersect(keep2,
               which(colnames(omics) %in% c(colM, colH)))
TH = intersect(keep2,
               which(colnames(omics) %in% c(colT, colH)))

```


## graph cor


"cor"  Plots a correlation network. Runs cov2cor if input is detected to be a covariance matrix and plots the input as is

"pcor" Plots a partial correlation network, using cor2pcor from the parcor package (Kraemer, Schaefer and Boulesteix, 2009) on the input matrix


"glasso"  Will run EBICglasso to obtain an optimal sparse estimate of the partial correlation matrix using the glasso package (Friedman, Hastie and Tibshirani, 2011)



```{r, 063_omics.qgraph.tst, echo=TRUE}

cormat = cor(as.matrix(omics[, keep2]), use = 'na.or.complete')
qgraph::qgraph(cormat, 
               shape='circle', 
               posCol='darkred', 
               negCol='darkblue',
               layout='spring', 
               vsize = 4, 
               cut = 0.95, 
               details = TRUE, 
               curveAll = TRUE,
               title = 'Omics',
               minimum = 0.70,
               labels = colnames(omics[, keep2]),
               label.cex = 1.5)


```


For more options see <https://www.rdocumentation.org/packages/qgraph/versions/1.9.3/topics/qgraph>



```{r, session_info}

devtools::session_info()


```

