---
title: "Integration across different omics datasets"
author: "Andrej Blejec"
date: 07. 02. 2023
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: show
---

```{r Author:,echo=FALSE}
###############################################
##                                           ##
## (c) Andrej Blejec (andrej.blejec@nib.si)  ##
##                                           ##
###############################################
```

```{r include=FALSE, message=FALSE, warnings=FALSE, cache=FALSE}
require(knitr)
render_markdown()
opts_chunk$set( fig.path='./figs/'
    , tidy=FALSE)
opts_knit$set( concordance=TRUE
    , root.dir = getwd()
    , unnamed.chunk.label = "ch"
    , width = 70
)
opts_knit$get("root.dir")
```

```{r additional arguments, echo=FALSE, message=FALSE, warnings=FALSE}
addArgs <- NULL
addArgs[1] <- c("")[1]
```

# Introduction

[Needs more text]  

In this document we present a work-flow for ntegration across different omics datasets.

[Note] This is not the final version of the document.

# File management system

Files are managed under the pISA-tree framework. To take advantage of pISA-tree metadata information, we will use package `pisar` (For installation from GitHub see [pisar](https://github.com/NIB-SI/pisar)).
```{r}
library(pisar)
pisa <- pisa()
# Set output directory (needed for .Rmd -> HTML)
pisa$oroot <- file.path(.aroot,"output")
.oroot <- pisa$oroot
```

```{r set specific arguments,results='hide',message=FALSE,warning=FALSE,echo=FALSE}
# Argumenti
# 1. Ime izvorne datoteke za analizo
# 2. Izbira genov (ime stolpca v featuredata)
#
 .callName <- addArgs[1]
 .vzorci <- addArgs[2]
#getwd()
#args
```

```{r initialize,echo=FALSE,include=FALSE,message=FALSE,warning=FALSE}
options(width=70)
#library(Hmisc)
#library(amisc)
#library(Biobase)
#library(xlsReadWrite)
#library(xtable)
#library(MASS)
catln <- function(...) cat(...,"\n")
```

Final document is in subdirectory `reports`:
```{r }
basename(outputFile)
```

## Info from pISA structure

Input/data directory

```{r }
.inroot
```

Results directory

```{r }
.oroot
```

```{r echo=FALSE}
catln("project:\t",     .pname)
catln("Investigation: ",.iname)
catln("Study:         ",.sname)
catln("Assay:         ",.aname)
```

# Packages and functions

%For canonical correlation analysis we will use package \pkg{CCA}, which is used in our projects.
%```{r message=FALSE,warning=FALSE}
%library(CCA)
%```

A package with regularized CCA and multiomics DIABLO method is *mixOmics*. Package *igraph* is needed for network analysis.

```{r message=FALSE,warning=FALSE}
library(mixOmics)
library(igraph)
```

Package for complex heatmaps.
```{r message=FALSE,warning=FALSE}
#BiocManager::install("ComplexHeatmap")
library(ComplexHeatmap)
# https://www.rdocumentation.org/packages/pheatmap/versions/1.0.12/topics/pheatmap
library(pheatmap)
```

## Functions

Some original and adapted functions can be found in the file that is silently processed here.

%% Additional functions
```{r result='hide'}
out <- ""
out <- paste(out,knit_child("005-Functions.Rmd", quiet=TRUE))
```




# Data

It is advisable to first read phenodata and featuredata, followed by actual data input. This enables smart selection of samples, based on the sample selection column with the assay name.

## Phenodata

```{r }
(pfn <- getMeta(.ameta
    , "Phenodata"))
dir(file.path(.aroot,dirname(pfn)), pattern = basename(pfn))
phdata <- read.table(file.path(.aroot,pfn)
  , header = TRUE
  ,  sep = "\t"
  , stringsAsFactors = FALSE
  , row.names=1
  )
dim(phdata)
names(phdata)
```


Check and use the sample selection column, if present.
```{r }
.aname
selectId <- substr(gsub("-",".",.aname),2,nchar(.aname))
selectId <- .vzorci
selectId
if(selectId %in% names(phdata)) pdata <- phdata[!is.na(phdata[,selectId]),] else
pdata <- phdata
dim(pdata)
```

Overview of selected samples:

```{r }
table(pdata$Treatment, pdata$SamplingDay)
.treat <- unique(pdata$Treatment)
.days <- unique(pdata$SamplingDay)
.entry <- 0.5

```

```{r }
summary(pdata)
apply(pdata,2,function(x) summary(as.factor(x)))
```

## Featuredata

```{r }
(ffn <- getMeta(.ameta,"Featuredata"))
```

```{r }
if(ffn != "")
fdata <- read.table(file.path(.iroot,ffn)
    , sep = "\t"
    , header = TRUE
    , na.strings = c("", "-")
    , stringsAsFactors = FALSE
    , row.names = 1
    ) else fdata <- NULL
head(fdata)
```

First few columns, if present.

```{r }
fdata[,1:2]
```

## Process data files

For this project we aim to integrate several multi-omics datasets.
In assay metadata file keys for data files start with keyword 'Data'.
Extract object names from those lines.

```{r}
ind <- grep("^Data",.ameta[,1])
datanames <-  gsub("^Data (.*):$","\\1",.ameta[ind,]$Key)
datanames
```


Read data and assign  them to objects named by the second word in the key.
```{r}
cat("Created objects:\n\n")
for (i in ind) {
nm <- gsub("^Data (.*):$","\\1",.ameta[i,]$Key)
x <- read.table(file.path(.aroot,.ameta[i,]$Value), header=TRUE, sep="\t")
assign(nm,x)
catln("\nDataset:", ls(pattern=nm))
str(get(nm))
}
```

\section{Combine datasets}

Datasets for DIABLO need to be collected in a list, with rows corresponding to the same samples. The order of samples from shrinked phenodata will be enforced.

The first component of the list will be a grouping variable, indicating the conditions. We will create reasonable names for groups.

```{r}
sday <- paste0(0,pdata$SamplingDay)
len <- nchar(sday)
sday <- substr(sday,len-1,len)
what <- paste(pdata$Treatment,sday,sep="")
X <- list(status= what)
names(X[[1]]) <- rownames(pdata)
X
```

```{r}
table(pdata$SamplingDay, what)
```
Put datasets into list X and ensure that they all have same order of samples, as in phenodata.
```{r}
datanames
for(i in 1:length(datanames)){
x <- get(datanames[i])
rownames(x) <- x[,1]
x <- x[,-1]
X[[i+1]] <- x[rownames(pdata),]
names(X)[i+1] <- datanames[i]
}
str(X)
names(X)
```

Same sample names?

```{r}
OK <- TRUE
for(i in 2:length(X)) {
print(ok <- all(names(X[[1]])==rownames(X[[i]])))
OK <- OK&ok
}
```

```{r, echo=FALSE, results='asis'}
if(OK) catln("Sample names in datasets match.") else catln("ERROR: Sample names in datasets do not match!!")
```

Put data into safe object `DATAall`.

```{r}
DATAall <- X
DATA <- X
```

We will also need the names of treatment groups.

```{r}
groups <- unique(pdata$Treatment)
groups
```



# Multiomics data integration with DIABLO



```{r}
CCDATA <- DATA
names(CCDATA)
```



```{r}
write("Entering 035-DIABLO !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!", "bla.log", append=!TRUE)
write(.oroot, "bla.log", append=TRUE)
write(pisa$oroot, "bla.log", append=TRUE)
write(commandArgs(trailingOnly = TRUE), "bla.log",append=TRUE)

```

```{r diablo, results='asis'}
out <- ""
out <- paste(out,knit_child("035-DIABLO-2.Rmd", quiet=TRUE))
cat(out)
```

```{r}
write("From 035-DIABLO !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!", "bla.log", append=TRUE)
```



# Metadata files

## Project

```{r pmeta, echo=FALSE,results='asis'}
.pmeta
```

## Investigation

```{r imeta, echo=FALSE,results='asis'}
.imeta
```

## Study

```{r smeta, echo=FALSE,results='asis'}
.smeta
```

## Assay

```{r ameta, echo=FALSE,results='asis'}
.ameta
```

# SessionInfo

```{r sessionInfo,results='asis',echo=FALSE}
cat(win.version(),"<br>")
sessionInfo()
prefix <- "<a href='file:///"
suffix <- "/</a><br>"
sdir <- gsub("/","/<br> ",dirname(getwd()))
#cat("Project path:<br>",sdir,"<br>")
args <- commandArgs(trailingOnly = TRUE)
mainFile <- basename(args[1])
#
mainFilePath <- file.path("../doc", mainFile)
mainFilePath <- gsub("/./","/",mainFilePath)
projectName <- rev((strsplit(dirname(getwd()), "/"))[[1]])[1]
#
sdir <- dirname(getwd())
sdir <- strsplit(sdir,split="/")[[1]]
cdir <- sapply(1:length(sdir),function(x) paste(sdir[1:x],collapse="/"))
#
#cat("<br>Project path: [\\href{run:",
#dirname(getwd()),
#"}{link}]\\\\<br>",sep="")
##

cat("<br>Local project path:<br><br>")
for(i in 1:length(sdir)) cat(
   prefix, cdir[i], "'>", sdir[i],suffix, "<wbr>\n",sep=""
   )

cat("<br>Links to project on GitHub:<br><br>")
ind <- grep("^_",sdir)
rind <- ind[1]-1

prefix <- "<a href='https://github.com/NIB-SI/"
cat("<ul>\n")
cat("<li>",
   file.path(prefix, sdir[rind]), "'>", sdir[rind],suffix, "</li>\n",sep=""
   )
for(i in 1:length(ind))  cat("   *  ",
   file.path(prefix, sdir[rind], "tree/main", paste(sdir[ind[1:i]], collapse="/")), "'>", sdir[ind[i]],suffix, "\n",sep=""
   )

cat("<ul><br>\n")

# <a href="file:///C:\Programs\sort.mw">Link 1</a>
cat("<br>Main file :`", mainFilePath, "`<br>")
#
mainFile <- strsplit(mainFile,'.',fixed=TRUE)[[1]][1]
projectName <- rev((strsplit(dirname(getwd()), "/"))[[1]])[1]
#cat("Project file: [\\href{run:",
#file.path(dirname(getwd()),paste0(projectName,".prj")),
#"}{link}]<br>",sep="")
#
``` 